---
title: "Analysis"
output: html_notebook
---
```{r setup}
library(lubridate)
library(tidyverse)
library(ggplot2)
```

Pull file
```{r}
atlantic_croaker_final <- read_csv("data/atlantic_croaker_final.csv")
View(atlantic_croaker_final)
```

Make new columns to answer hypothesis
```{r}
atlantic_croaker_final <- atlantic_croaker_final %>% 
  mutate(aspect_ratio=(Caudheight/Caudarea)^(1/2), square_caudal_peduncle_depth_factor=(Cauddepth/Depthatpec)^2, 
         Year=year(Tow_date))
View(atlantic_croaker_final)
```

Structure
1. Type question
2. Make plot
3. Run statistical test
4. Answer question

#Question set to answer first main question relating morphological traits within the years/location

Hypothesis:
Fish from 1995 will have a higher total length and aspect ratio, and a lower square caudal peduncle depth factor compared to fish from 2017. 

```{r}
#Make dataframe for 1995 & 2017 fish
##in order to create statistical tests
atcroaker95 <- atlantic_croaker_final %>% 
  filter(Year==1995)

atcroaker17 <- atlantic_croaker_final %>% 
  filter(Year==2017)
```

Question 1:
Is aspect ratio higher in fish from 1995 than fish from 2017?
```{r}
#Making a plot
ggplot(data= atlantic_croaker_final, aes(x=aspect_ratio)) +
  geom_histogram() +
  facet_wrap(~Year)

ggplot(data=atlantic_croaker_final) +
  geom_boxplot(aes(x=Year, y=aspect_ratio, group= Year))

#Statistical test
wilcox.test(x=atcroaker95$aspect_ratio, y=atcroaker17$aspect_ratio, alternative = c("two.sided"))
```

Question 2:
Does fish from 1995 have a higher total length measurement than fish from 2017?
```{r}
#Make a plot
ggplot(data= atlantic_croaker_final, aes(x=Totallength)) +
  geom_histogram() +
  facet_wrap(~Year)

ggplot(data=atlantic_croaker_final) +
  geom_boxplot(aes(x=Year, y=Totallength, group= Year))

#Statistical analysis
wilcox.test(x=atcroaker95$Totallength, y=atcroaker17$Totallength , alternative=c("two.sided"))
```

Question 3:
Is square caudal peduncle depth factor lower in fish from 1995 than fish from 2017?
```{r}
#Make a plot
ggplot(data= atlantic_croaker_final, aes(x=square_caudal_peduncle_depth_factor)) +
  geom_histogram() +
  facet_wrap(~Year) 

ggplot(data=atlantic_croaker_final) +
  geom_boxplot(aes(x=Year, y=square_caudal_peduncle_depth_factor, group= Year))

#Statistical analysis
wilcox.test(x=atcroaker95$square_caudal_peduncle_depth_factor,  y=atcroaker17$square_caudal_peduncle_depth_factor, alternative = c("two.sided"))
```

#Question set 2 relating morphological traits and temperature within the years

Question 1
Aspect ratio
```{r}
#Linear model
AR_linearmodel <- lm(aspect_ratio ~ SST, atlantic_croaker_final)
summary(AR_linearmodel)

#Plot
ggplot(data=atlantic_croaker_final) +
  geom_point(aes(x=SST, y=aspect_ratio, color=factor(Year))) +
  geom_smooth(aes(x=SST, y=aspect_ratio), method = "lm")
```
p-value: 0.001113

Question 2
Total length
```{r}
#Linear model
TL_linearmodel <- lm(Totallength ~ SST, atlantic_croaker_final)
summary(TL_linearmodel)

#Plot
ggplot(data = atlantic_croaker_final) +
  geom_point(aes(x=SST, y=Totallength, color= factor(Year))) +
  geom_smooth(aes(x= SST,y=Totallength), method = "lm")
```
p-value: 0.3649
not a significant relationship

Question 3
Square caudal peduncle depth factor
```{r}
#Linear model
CPDF_linearmodel <- lm(square_caudal_peduncle_depth_factor ~ SST, atlantic_croaker_final) 
summary(CPDF_linearmodel)

#Plot
ggplot(data=atlantic_croaker_final) +
  geom_point(aes(x= SST, y=square_caudal_peduncle_depth_factor, color=factor(Year))) +
  geom_smooth(aes(x=SST, y= square_caudal_peduncle_depth_factor), method = "lm")
```
p-value: 0.03942
