---
title: "Data cleaning"
output: html_notebook
---

Put data files from csv and clean it and later merge it into a data frame.
```{r setup}
library(lubridate)
library(tidyverse)
```

Pull the csv with the measurements
Made a csv using ObjectJ plugin, taking measurements of the specimens from 1995
Odd rows are measurements from the lateral photos and the even rows are measurements from dorsal photos
```{r}
atlantic_croaker_1995_measurements <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/data/atlantic_croaker_1995_measurements.csv")
View(atlantic_croaker_1995_measurements)
```

Eliminate a column
```{r}
atlantic_croaker_1995_measurements <- atlantic_croaker_1995_measurements %>% 
  mutate(spp_num=rep(1:(nrow(atlantic_croaker_1995_measurements)/2), each=2))
view(atlantic_croaker_1995_measurements)

#Merge data
atlantic_croaker_1995_measurements.r <- atlantic_croaker_1995_measurements %>% 
  group_by(spp_num) %>% 
  summarise(across(2:14, ~ max(.x, na.rm=TRUE)))
```

Pull in data sheet 
```{r}
DataSheetPhotos_1995_Micro_undu_only <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/data/DataSheetPhotos_1995_Micro_undu_only.csv")
View(DataSheetPhotos_1995_Micro_undu_only)

#Removed row 117 due to fish lost 
DataSheetPhotos_1995_Micro_undu_only <- DataSheetPhotos_1995_Micro_undu_only %>% 
  filter(Code!="00916")
```

Add new column to pull out the code column 
```{r}
atlantic_croaker_1995_measurements.r <- atlantic_croaker_1995_measurements.r %>% 
  mutate(Code=DataSheetPhotos_1995_Micro_undu_only$Code)
```

Combine the two data sheets as one
```{r}
atlantic_croaker_1995_mphotos <- left_join(atlantic_croaker_1995_measurements.r, DataSheetPhotos_1995_Micro_undu_only, by= "Code")
```

Add the temperature sheet
```{r}
icthy_data <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/data/icthy_data.csv")
View(icthy_data)
```

See the structures
```{r}
str(atlantic_croaker_1995_mphotos)
str(icthy_data)
```

Make new data frame and delete some columns
```{r}
cols_drop <- c("FL", "SL", "TL")
icthy_data_reduced <- icthy_data %>% 
  select(-any_of(cols_drop)) %>% 
  rename(Tow_date=Date) %>% 
  mutate(Tow_date=(ymd(Tow_date))) %>% 
  rename(Tow_ID=Tow)
```

Change column names from one data set to another
```{r}
atlantic_croaker1995_measuremts <- atlantic_croaker_1995_mphotos %>% 
  rename(Tow_date=`Tow Date`) %>% 
  mutate(Tow_date=(mdy(Tow_date)))
```

Merge data sheets
```{r}
atlantic_croaker1995 <- inner_join(atlantic_croaker1995_measuremts, icthy_data_reduced, by=c("Tow_date", "Tow_ID"))
```

Link to time data/temperature
```{r}
env_1995 <- read_csv("data/env_1995.csv")
View(env_1995)

#rename date first 
env_1995 <- env_1995 %>% 
  rename(Tow_date=Date)

#join 
atlantic_croaker1995 <- inner_join(atlantic_croaker1995, env_1995, by="Tow_date")
```

Filter one species to the data sheet
```{r}
atlantic_croaker1995 <- atlantic_croaker1995 %>% 
  filter(Species=="undulatus") %>%
  unique()
```

Save
```{r}
write_csv(atlantic_croaker1995, file="data/atlantic_croaker1995.csv")
```

mutate=create a new column
filter= select specific rows we want to keep