---
title: "Data cleaning- Justin photos"
output: html_notebook
---

```{r setup }
library(lubridate)
library(tidyverse)
library(ggplot2)
```

Pull Justin's measurements
```{r}
NJ_data_final_JD <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/data/NJ_data_final_JD.csv")
View(NJ_data_final_JD)
```

Pull 1995 measurements
```{r}
atlantic_croaker1995 <- read_csv("data/atlantic_croaker1995.csv")
```

Pull the csv files with Justin's photos which I measured
The odd rows represent measurements from the lateral side of the fish, and the even rows represent measurements from the dorsal side of the fish
```{r}
atlantic_croaker_2017_Jmeasurements <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/data/atlantic_croaker_2017_Jmeasurements.csv")
View(atlantic_croaker_2017_Jmeasurements)
```

Create column to then merge them
```{r}
atlantic_croaker2017_justin_measurements <- atlantic_croaker_2017_Jmeasurements %>% 
  mutate(spp_num=rep(1:(nrow(atlantic_croaker_2017_Jmeasurements)/2), each=2))
  
#merged the two columns 
atlantic_croaker2017JM <- atlantic_croaker2017_justin_measurements %>% 
  group_by(spp_num) %>% 
  summarise(across(2:14,~ max (.x, na.rm=TRUE)))

#copying linked image file names from ObjectJ
linked_image_names <- c(seq(272,290, by = 1), 314)
```

Add the code (id name of each fish) to the sheet I created
```{r}
atlantic_croaker2017J_M <- atlantic_croaker2017JM %>% 
  mutate(Code=linked_image_names)
```

Add _Justin to the measurements
```{r}
atlantic2017_justin <- NJ_data_final_JD %>% 
  rename_with(~ paste(.x, "_Justin", sep=""),.cols=c(2:14))
```

Merge columns together
```{r}
atlantic_croaker2017 <- inner_join(atlantic2017_justin, atlantic_croaker2017J_M, by="Code")
```

Code used: colnames(atlantic_croaker2017J_M)
 "Standardlength"   "Totallength"      "Depthatpec"       "Depthatanus"     
 "Pulsearea"        "Musclearea"       "Bodyarea"         "Cauddepth"        "Caudheight"      
 "Caudarea"         "Bodywidth"        "Interoctdistance" "Eyediameter"        


#Start creating the linear models

##Standard Length
```{r standard length}
SL_linear_model <- lm(Standardlength ~ standardlength_Justin, atlantic_croaker2017)
summary(SL_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=standardlength_Justin, y=Standardlength)) +
  geom_smooth(aes(x=standardlength_Justin, y=Standardlength), method = "lm")+
  geom_abline(intercept=0, slope=1) +
  ggtitle("Fish standard length measurements")
```
Information recorded from the linear model
y=mx+b
m= 1.1178x-0.9465
R-squared= 0.8659
P value= 2.78e-09

##Total Lenght
```{r}
TL_linear_model <- lm(Totallength ~ totallength_Justin, atlantic_croaker2017)
summary(TL_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=totallength_Justin, y=Totallength)) +
  geom_smooth(aes(x=totallength_Justin, y=Totallength), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish total length measurements")
```
y=mx+b
m= 1.11796-1.27534
R-squared= 0.8764
P value= 1.32e-09

##Depth Pectoral
```{r}
DP_linear_model <- lm(Depthatpec ~ bodydepthpectoral_Justin, atlantic_croaker2017)
summary(DP_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=bodydepthpectoral_Justin, y=Depthatpec))+
  geom_smooth(aes(x=bodydepthpectoral_Justin, y=Depthatpec), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Depth Pectoral Measurements")
```
y=mx+b
m= 1.16066-0.45649
R-squared=0.9164
P value=3.86e-11

##Depth Anus
```{r}
DA_linear_model <- lm(Depthatanus ~ bodydepthanus_Justin, atlantic_croaker2017)
summary(DA_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x= bodydepthanus_Justin, y=Depthatanus)) +
  geom_smooth(aes(x= bodydepthanus_Justin, y=Depthatanus), method = "lm")+
  geom_abline(intercept = 0, slope=1) +
  lims(x=c(0,max(atlantic_croaker2017$bodydepthanus_Justin)),y=c(0, max(atlantic_croaker2017$Depthatanus))) +
  ggtitle("Fish Depth at Anus Measurements")
```
y=mx+b
m=0.9988-0.3047
R-squared=0.8441
P value=1.09e-08

##Propulsive Area
```{r}
PA_linear_model <- lm(Pulsearea ~ propulsivearea_Justin, atlantic_croaker2017)
summary(PA_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017)+
  geom_point(aes(x=propulsivearea_Justin, y=Pulsearea)) +
  geom_smooth(aes(x=propulsivearea_Justin, y=Pulsearea), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Propulsive Area Measurements")
```
y=mx+b
m= 1.124-1.847
R-squared= 0.8598
P value= 4.14e-09

##Muscle Area
```{r}
MA_linear_model <- lm(Musclearea ~ musclearea_Justin, atlantic_croaker2017)
summary(MA_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=musclearea_Justin, y=Musclearea)) +
  geom_smooth(aes(x=musclearea_Justin, y=Musclearea), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Muscle Area Measurements")
```
y=mx+b
m= 1.12668-0.82451
R-squared= 0.9078
P value= 9.33e-11

##Body Area
```{r}
BA_linear_model <- lm(Bodyarea ~ bodyarea_Justin, atlantic_croaker2017)
summary(BA_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=bodyarea_Justin, y=Bodyarea)) +
  geom_smooth(aes(x=bodyarea_Justin, y=Bodyarea), method="lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Body Area Measurements")
```
y=mx+b
m=1.08743-1.04866
R-squared=0.8707
P value=1.99e-09

##Caudal Peduncle Depth
```{r}
CP_linear_model <- lm(Cauddepth ~ caudalpeduncledepth_Justin, atlantic_croaker2017)
summary(CP_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=caudalpeduncledepth_Justin, y=Cauddepth)) +
  geom_smooth(aes(x=caudalpeduncledepth_Justin, y=Cauddepth), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Caudal Peduncle Depth Measurements")
```
y=mx+b
m= 1.029639 + 0.006023
R-squared= 0.7838
P value= 2.14e-07

##Caudal Fin Height
```{r}
CF_linear_model <- lm(Caudheight ~ caudalfinheight_Justin, atlantic_croaker2017)
summary(CF_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=caudalfinheight_Justin, y=Caudheight)) +
  geom_smooth(aes(x=caudalfinheight_Justin, y=Caudheight), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Caudal Fin Height Measurements")
```
y=mx+b
m= 0.6657 + 0.2973
R-squared= 0.5838
P value= 8.8e-05

##Caudal Fin Area
```{r}
CA_linear_model <- lm(Caudarea ~ caudalfinarea_Justin, atlantic_croaker2017)
summary(CA_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=caudalfinarea_Justin, y=Caudarea)) +
  geom_smooth(aes(x=caudalfinarea_Justin, y=Caudarea), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Caudal Fin Area Measurements")
```
y=mx+b
m=0.6457 + 0.3727
R-squared=0.5273
P value= 0.000289

##Body Width
```{r}
BW_linear_model <- lm(Bodywidth ~ bodywidth_Justin, atlantic_croaker2017)
summary(BW_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=bodywidth_Justin, y=Bodywidth)) +
  geom_smooth(aes(x=bodywidth_Justin, y=Bodywidth), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  lims(x=c(0, max(atlantic_croaker2017$bodywidth_Justin)), y=c(0, max(atlantic_croaker2017$Bodywidth)))
  ggtitle("Fish Body Width Measurements")
```
y=mx+b
m=0.6886-0.2114
R-squared= 0.6553
P value=1.54e-05

##Eye Diameter
```{r}
ED_linear_model <- lm(Eyediameter ~ eyediameter_Justin, atlantic_croaker2017)
summary(ED_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=eyediameter_Justin, y=Eyediameter)) +
  geom_smooth(aes(x=eyediameter_Justin, y=Eyediameter), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Eye Diameter Measurements")
```
y=mx+b
m= 1.13797-0.09974
R-squared=0.7198
P value= 2.29e-06

##Interorbital Width
```{r}
IW_linear_model <- lm(Interoctdistance ~ interorbitalwidth_Justin, atlantic_croaker2017)
summary(IW_linear_model)

#make a ggplot
ggplot(atlantic_croaker2017) +
  geom_point(aes(x=interorbitalwidth_Justin, y=Interoctdistance)) +
  geom_smooth(aes(x=interorbitalwidth_Justin, y=Interoctdistance), method = "lm") +
  geom_abline(intercept = 0, slope = 1) +
  ggtitle("Fish Interorbital Width Measurements")
```
y=mx+b
m= 0.9007 + 0.1275
R-squared= 0.5505
P value= 0.00018


# Converting Justin's measurements from 2017 to Jesenia's measurements
colnames(atlantic_croaker1995)
 [1] "spp_num"          "Standardlength"   "Totallength"      "Depthatpec"       "Depthatanus"     
 [6] "Pulsearea"        "Musclearea"       "Bodyarea"         "Cauddepth"        "Caudheight"      
[11] "Caudarea"         "Bodywidth"        "Interoctdistance" "Eyediameter"      "Code"            
[16] "Spp"              "Tow_date"         "Tow_ID"           "Tow_num"          "Picture Date"    
[21] "Time Start-End"   "Notes"            "Measurements"     "Genus"            "Species"         
[26] "Survey"           "Preserve"         "Number"           "Location"        

colnames(atlantic2017_justin)
 [1] "Code"                       "standardlength_Justin"     
 [3] "totallength_Justin"         "bodydepthpectoral_Justin"  
 [5] "bodydepthanus_Justin"       "propulsivearea_Justin"     
 [7] "bodyarea_Justin"            "musclearea_Justin"         
 [9] "eyediameter_Justin"         "caudalpeduncledepth_Justin"
[11] "caudalfinheight_Justin"     "caudalfinarea_Justin"      
[13] "bodywidth_Justin"           "interorbitalwidth_Justin"  
[15] "Date"                       "region"                    
[17] "SST"    

```{r}
#Format
at_croaker2017 <- atlantic2017_justin %>% 
  mutate(Standardlength= 1.1178*standardlength_Justin - 0.9465,
         Totallength=1.11796*totallength_Justin -1.27534,
         Depthatpec= 1.16066*bodydepthpectoral_Justin -0.45649,
         Depthatanus= 0.9988*bodydepthanus_Justin -0.3047,
         Pulsearea= 1.124*propulsivearea_Justin -1.847,
         Musclearea=1.12668*musclearea_Justin -0.82451,
         Bodyarea= 1.08743*bodyarea_Justin -1.04866,
         Cauddepth= 1.029639*caudalpeduncledepth_Justin + 0.006023,
         Caudheight= 0.6657*caudalfinheight_Justin + 0.2973,
         Caudarea= 0.6457*caudalfinarea_Justin + 0.3727,
         Bodywidth= 0.6886*bodywidth_Justin -0.2114,
         Eyediameter= 1.13797*eyediameter_Justin -0.09974,
         Interoctdistance= 0.9007*interorbitalwidth_Justin + 0.1275, 
         Spp= "Micropogonias undulatus") %>% 
  rename(Tow_date=Date) %>% 
  select(Spp, Tow_date, Code, Standardlength, Totallength, Depthatpec, Depthatanus, Bodyarea, Musclearea, Pulsearea, Bodywidth, Caudarea, Cauddepth, Caudheight, Eyediameter, Interoctdistance, SST)

view(at_croaker2017)
```

colnames(atlantic_croaker1995)
 [1] "spp_num"          "Standardlength"   "Totallength"      "Depthatpec"       "Depthatanus"     
 [6] "Pulsearea"        "Musclearea"       "Bodyarea"         "Cauddepth"        "Caudheight"      
[11] "Caudarea"         "Bodywidth"        "Interoctdistance" "Eyediameter"      "Code"            
[16] "Spp"              "Tow_date"         "Tow_ID"           "Tow_num"          "Picture Date"    
[21] "Time Start-End"   "Notes"            "Measurements"     "Genus"            "Species"         
[26] "Survey.x"         "Preserve"         "Number"           "Location.x"       "...30"           
[31] "Survey.y"         "Location.y"       "Time"             "Sudo"             "Bodo"            
[36] "SuSal"            "BoSal"            "SuTemp"           "BoTemp"           "Tide"            
[41] "Depth"            "LatDeg"           "Latitude"         "LongDeg"          "LONGITUD"        
[46] "Secchi"           "SuPH"             "BoPH"             "Northing"         "Easting"         
[51] "UTM"              "Edit"             "year"          

 colnames(at_croaker2017)
[1] "Spp"              "Tow_date"         "Code"             "Standardlength"   "Totallength"     
[6] "Depthatpec"       "Depthatanus"      "Bodyarea"         "Musclearea"       "Pulsearea"       
[11] "Bodywidth"        "Caudarea"         "Cauddepth"        "Caudheight"       "Eyediameter"     
[16] "Interoctdistance" "SST" 

Create a new file that has the temperature in it
```{r}
atlantic_1995_croaker <- atlantic_croaker1995 %>% 
  rename(SST=SuTemp) %>% 
  select(Spp, Tow_date, Code, Standardlength, Totallength, Depthatpec, Depthatanus, Bodyarea, Musclearea, Pulsearea, Bodywidth, Caudarea, Cauddepth, Caudheight, Eyediameter, Interoctdistance, SST)
View(atlantic_1995_croaker)
```

See if both columns match names
```{r}
colnames(atlantic_1995_croaker)==colnames(at_croaker2017)
```


```{r}
atlantic_croaker_final <- rbind(atlantic_1995_croaker, at_croaker2017)
view(atlantic_croaker_final)
```

Save data in files
```{r}
write_csv(atlantic_croaker_final, file= "data/atlantic_croaker_final.csv")
```

