---
title: "Practice Data Analysis Larval Traits"
output: html_notebook
---

Here we will practice some analyses to use on the larval fish morphology data. 

We're using a R Markdown Document. Here (in the white space) we can type normally. Within chunks (grey) we have to start the line with a hash (#) to type normal text as notes. If we don't use a hash (#) R will try to run it as code. 

In order to best understand this code, I recommend running it line by line. As long as your cursor is on a line of code, that code will run if you 'control'+'return'. Alternatively, you can run code by using the -->Run button in the top right corner of this window. All code that you run will show up in your Console below, but will only be accessible later if it is saved in this R Markdown Document. 

Want to learn more about R Markdown Documents? This is a helpful video. https://www.youtube.com/watch?v=tKUufzpoHDE

To insert a new chunk, click the green +C button up top, or press option, command, 'i'. 

Each chunk needs to have language (r for us) and a name of what's happening with no symbols in the first line within the brackets. For example, in the first one it is {r setup}. You can't repeat the name of what's happening in chunks. 

```{r setup}
#load packages or apps using library() function. This takes the package off your shelf and allows you to use it

library(lubridate)
library(tidyverse) 

#if you don't have a package installed, you'll have to do that first by using the install.packages() function, making sure the package name is in quotes
```

Bring in data stored as csvs (Comma Separated Values)

- Be sure that the csvs do not have any "-" or "," which will make it hard for R to parse the data as it comes into R from the csv

- Any empty cell should be filed with 'NA'

```{r load csvs}
photos <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/tutorials/DataSheetPhotos_Practice.csv")

measurements <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/tutorials/Measurements_practice.csv")

icthy_data <- read_csv("~/Documents/OneDrive - aguadilla.inter.edu/BS Microbiology Inter/Internship and opportunities/RISE Internship/2022-croakerlarvae-rise/tutorials/icthy_data_Practice.csv")


```

Now we've loaded in three CSVs to data frames. You'll see them in your Environment in the top right. 

Now, let's take a look at these! 
```{r looking at data frames}
View(photos) #let's view it like a spreadsheet above
summary(photos) #overall summary and statistics
str(photos) #structure, are the columns in the right format?

#check this out for all of the data frames
#numerical columns should be <int> or <dbl>
#character columns should be <chr>

```
It appears that the photos data frame has some extra useless columns, let's delete those
```{r delete extra columns }
View(photos)
#keep columns 1:7
photos_reduced <- photos[,1:7] #this tells us to make a new data frame extracting all rows from columns 1:7 (column = after comma, row = before comma]) in photos data frame

View(photos_reduced)
```

We also don't want the data from icthy_data that's not for our focal species
```{r}
summary(factor(icthy_data$Species))

icthy_data_reduced <- icthy_data %>% #first, access icthy_data
  filter(Species == "undulatus") #then, filter out only rows where Species is undulatus

summary(factor(icthy_data_reduced$Species)) #success!
```


We now need to merge these data frames together, which columns are the same across data frames?

```{r check column names}
colnames(photos_reduced)
colnames(measurements)
colnames(icthy_data_reduced)

#it can also be helpful to look at the first few rows
head(photos_reduced)
head(measurements)
head(icthy_data_reduced)

#check that all date columns are correctly formatted
photos_reduced$Tow_Date <- mdy(photos_reduced$Tow_Date) #tells R to interpret this column as a date in month, day, year format

#note that $ calls a specific column. RStudio is awesome, because once you start typing a column name it will give you options in a drop down menu

head(photos_reduced) #note it now says <date> under Tow.Date

```

Match Spp to Genus Spp
-In photos_reduced, species is under spp, but in icthy data species is under genus and species, we have to match them
```{r matching spp genus}
#make new Species column in photos_reduced data frame
photos_reduced$Species <- as.factor(word(photos_reduced$Spp,2,2, sep = " ")) #pull out species

#want to know how this is working? run this line, and look at help panel in bottom right
?word

#make new Genus column in photos_reduced data frame
photos_reduced$Genus <- as.factor(word(photos_reduced$Spp,1,1, sep = " "))
  
```

Now, I've noticed that we use Tow_ID in photo data frame, but Tow in icthy_data_reduced data frame, let's match these so that they can help link the two data frames

```{r tow tow_id}
icthy_data_reduced$Tow_ID <- icthy_data_reduced$Tow
```

Time to merge! 

```{r merge}
icthy_data_photos <- inner_join(photos_reduced, icthy_data_reduced, by = c("Tow_ID", "Species", "Genus")) #first merge

full_merge_icthyoplankton <- inner_join(icthy_data_photos, measurements, by = c("Code"))

View(full_merge_icthyoplankton)
nrow(full_merge_icthyoplankton)
```

#Now it's time for analyses
A good way to  start each analysis is to ask a specific question. 

1. How does sample # change by date and location for each species?
```{r sample versus date}
ggplot(data = full_merge_icthyoplankton) + #here, you identify which data frame has the data you want to plot
  geom_point(aes(x = Tow_Date, y = Number, color = Species)) + #always set your variables within aes() which stands for 'aesthetics'
  facet_wrap(~Location) + #adds separate plots for separate locations
  theme_classic()
```
2. Does standard length vary by date? Is this pattern different for different locations and species?
```{r traits versus dates}
ggplot(data = full_merge_icthyoplankton) +
  geom_boxplot(aes(x= Tow_Date, y = SL, color = Species)) +
  facet_wrap(~Location) +
  theme_classic()

summary(full_merge_icthyoplankton)

full_merge_icthyoplankton
```
3. Now, we can ask a ton of different questions. Ask a few yourself! 

Variables to include:
- Species
- Location
- Morphological traits
- Number of fish
- Temperature
- Date

```{r}


```

